---
title: "Analyses of the Memory Data"
author: Hector Bahamonde
date: March 17th, 2017
output: 
  html_document: 
    toc: true
    toc_float: true
  theme: cosmo
  fig_caption: yes
  fontsize: 9pt
---

<style type="text/css">


html{
    width:100%;
    height:100%;
}

body{ /* Normal  */
   font-size: 12px;
   width: 100%;
   height: 100%;
}
td {  /* Table  */
   font-size: 8px;
}
h1 { /* Header 1 */
 font-size: 28px;
 color: DarkBlue;
}
h2 { /* Header 2 */
 font-size: 22px;
 color: DarkBlue;
}
h3 { /* Header 3 */
 font-size: 18px;
 color: DarkBlue;
}
code.r{ /* Code block */
  font-size: 10px;
}
pre { /* Code block */
  font-size: 10px
}
</style>

```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Loading the Data
cat("\014")
rm(list=ls())
setwd("/Users/hectorbahamonde/RU/RA/Rick_Lau/Memory_Data")

## Load the data
load("/Users/hectorbahamonde/RU/RA/Rick_Lau/Memory_Data/Hector.rdata") ; dat = Hector

## recode

### generating MTurk dummy (MTurk=1, 0 otherwise)
dat$MTurk = as.numeric(dat$StudentParent == 3)
dat$MTurk <- ordered(as.factor(dat$MTurk), levels = c(0,1), labels = c("Rutgers", "MTurk"))


### recoding StudentParent
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(plyr)

dat$StudentParent = mapvalues(
        dat$StudentParent,
        from = c(
                levels(as.factor(dat$StudentParent))[1],
                levels(as.factor(dat$StudentParent))[2],
                levels(as.factor(dat$StudentParent))[3]), # 3 (for MTurk) will be NA
        to = c("Student", "Parent", NA))
```


##### Notes

- ```Age```, ```YrsEduc```, ```PolSoph```, ```LibCon``` were rescaled. The new range goes from -.5 to .5. The variables used in the models were also rescaled.
- Now variable ```StudentParent``` has two values, and the following N:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(dat$StudentParent)
```

- New variable ```MTurk``` has two values, and the following N:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(dat$MTurk)
```

```{r , message=FALSE, warning=FALSE, echo=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(scales)


## Rescaling all variables to be used in the models
dat$DSmithMemAff5 = rescale(dat$DSmithMemAff5, to = c(-.5, .5))
dat$DSmithMemAff50 = rescale(dat$DSmithMemAff50, to = c(-.5, .5))
dat$DSmithIWMemAff5 = rescale(dat$DSmithIWMemAff5, to = c(-.5, .5))
dat$DSmithAccRecogMemAff5 = rescale(dat$DSmithAccRecogMemAff5, to = c(-.5, .5))
dat$DSmithDifAff = rescale(dat$DSmithDifAff, to = c(-.5, .5))
dat$DSmithIWDifAff = rescale(dat$DSmithIWDifAff, to = c(-.5, .5))
dat$DSmithMemAff = rescale(dat$DSmithMemAff, to = c(-.5, .5))
dat$DSmithMemAff0 = rescale(dat$DSmithMemAff0, to = c(-.5, .5))
dat$DSmithIWMemAff = rescale(dat$DSmithIWMemAff, to = c(-.5, .5))
dat$DSmithIWMemAff = rescale(dat$DSmithIWMemAff, to = c(-.5, .5))
dat$DSmithAccRecogMemAff10 = rescale(dat$DSmithAccRecogMemAff10, to = c(-.5, .5))
dat$DSmith25Cumu0 = rescale(dat$DSmith25Cumu0, to = c(-.5, .5))
dat$DSmithWk5WeeklyTally0 = rescale(dat$DSmithWk5WeeklyTally0, to = c(-.5, .5))
dat$DSmith25Cumu1 = rescale(dat$DSmith25Cumu1, to = c(-.5, .5))
dat$DSmithWk5WeeklyTally1 = rescale(dat$DSmithWk5WeeklyTally1, to = c(-.5, .5))
dat$DSmithWk25WeeklyPBTally1 = rescale(dat$DSmithWk25WeeklyPBTally1, to = c(-.5, .5))
dat$DSmithWk25WeeklyPBTally2 = rescale(dat$DSmithWk25WeeklyPBTally2, to = c(-.5, .5))
dat$DSmith25Cumu2 = rescale(dat$DSmith25Cumu2, to = c(-.5, .5))
dat$DSmithWk5WeeklyTally2 = rescale(dat$DSmithWk5WeeklyTally2, to = c(-.5, .5))
dat$DSmith29Cumu0 = rescale(dat$DSmith29Cumu0, to = c(-.5, .5))
dat$DSmithWk9WeeklyTally0 = rescale(dat$DSmithWk9WeeklyTally0, to = c(-.5, .5))
dat$DSmith29Cumu1 = rescale(dat$DSmith29Cumu1, to = c(-.5, .5))
dat$DSmithWk9WeeklyTally1 = rescale(dat$DSmithWk9WeeklyTally1, to = c(-.5, .5))
dat$DSmithWk29WeeklyPBTally1 = rescale(dat$DSmithWk29WeeklyPBTally1, to = c(-.5, .5))
dat$DSmithWk29WeeklyPBTally2 = rescale(dat$DSmithWk29WeeklyPBTally2, to = c(-.5, .5))
dat$DSmith29Cumu2 = rescale(dat$DSmith29Cumu2, to = c(-.5, .5))
dat$DSmithWk9WeeklyTally2 = rescale(dat$DSmithWk9WeeklyTally2, to = c(-.5, .5))
dat$DSmithMR29Cumu0 = rescale(dat$DSmithMR29Cumu0, to = c(-.5, .5))
dat$DSmithWk9MRWeeklyTally0 = rescale(dat$DSmithWk9MRWeeklyTally0, to = c(-.5, .5))
dat$DSmithMR29Cumu1 = rescale(dat$DSmithMR29Cumu1, to = c(-.5, .5))
dat$DSmithWk9MRWeeklyTally1 = rescale(dat$DSmithWk9MRWeeklyTally1, to = c(-.5, .5))
dat$DSmithMR29PB1 = rescale(dat$DSmithMR29PB1, to = c(-.5, .5))
dat$DSmithMR29Cumu2 = rescale(dat$DSmithMR29Cumu2, to = c(-.5, .5))
dat$DSmithWk9MRWeeklyTally2 = rescale(dat$DSmithWk9MRWeeklyTally2, to = c(-.5, .5))
dat$DSmithMR29PB2 = rescale(dat$DSmithMR29PB2, to = c(-.5, .5))
dat$DSmithAccAccessedRecogMemAff = rescale(dat$DSmithAccAccessedRecogMemAff, to = c(-.5, .5))
dat$DWilsonMemAff5 = rescale(dat$DWilsonMemAff5, to = c(-.5, .5))
dat$DWilsonMemAff50 = rescale(dat$DWilsonMemAff50, to = c(-.5, .5))
dat$DWilsonIWMemAff5 = rescale(dat$DWilsonIWMemAff5, to = c(-.5, .5))
dat$DWilsonAccRecogMemAff5 = rescale(dat$DWilsonAccRecogMemAff5, to = c(-.5, .5))
dat$DWilsonDifAff = rescale(dat$DWilsonDifAff, to = c(-.5, .5))
dat$DWilsonIWDifAff = rescale(dat$DWilsonIWDifAff, to = c(-.5, .5))
dat$DWilsonMemAff = rescale(dat$DWilsonMemAff, to = c(-.5, .5))
dat$DWilsonMemAff0 = rescale(dat$DWilsonMemAff0, to = c(-.5, .5))
dat$DWilsonIWMemAff = rescale(dat$DWilsonIWMemAff, to = c(-.5, .5))
dat$DWilsonIWMemAff = rescale(dat$DWilsonIWMemAff, to = c(-.5, .5))
dat$DWilsonAccRecogMemAff10 = rescale(dat$DWilsonAccRecogMemAff10, to = c(-.5, .5))
dat$DWilson25Cumu0 = rescale(dat$DWilson25Cumu0, to = c(-.5, .5))
dat$DWilsonWk5WeeklyTally0 = rescale(dat$DWilsonWk5WeeklyTally0, to = c(-.5, .5))
dat$DWilson25Cumu1 = rescale(dat$DWilson25Cumu1, to = c(-.5, .5))
dat$DWilsonWk5WeeklyTally1 = rescale(dat$DWilsonWk5WeeklyTally1, to = c(-.5, .5))
dat$DWilsonWk25WeeklyPBTally1 = rescale(dat$DWilsonWk25WeeklyPBTally1, to = c(-.5, .5))
dat$DWilsonWk25WeeklyPBTally2 = rescale(dat$DWilsonWk25WeeklyPBTally2, to = c(-.5, .5))
dat$DWilson25Cumu2 = rescale(dat$DWilson25Cumu2, to = c(-.5, .5))
dat$DWilsonWk5WeeklyTally2 = rescale(dat$DWilsonWk5WeeklyTally2, to = c(-.5, .5))
dat$DWilson29Cumu0 = rescale(dat$DWilson29Cumu0, to = c(-.5, .5))
dat$DWilsonWk9WeeklyTally0 = rescale(dat$DWilsonWk9WeeklyTally0, to = c(-.5, .5))
dat$DWilson29Cumu1 = rescale(dat$DWilson29Cumu1, to = c(-.5, .5))
dat$DWilsonWk9WeeklyTally1 = rescale(dat$DWilsonWk9WeeklyTally1, to = c(-.5, .5))
dat$DWilsonWk29WeeklyPBTally1 = rescale(dat$DWilsonWk29WeeklyPBTally1, to = c(-.5, .5))
dat$DWilsonWk29WeeklyPBTally2 = rescale(dat$DWilsonWk29WeeklyPBTally2, to = c(-.5, .5))
dat$DWilson29Cumu2 = rescale(dat$DWilson29Cumu2, to = c(-.5, .5))
dat$DWilsonWk9WeeklyTally2 = rescale(dat$DWilsonWk9WeeklyTally2, to = c(-.5, .5))
dat$DWilsonMR29Cumu0 = rescale(dat$DWilsonMR29Cumu0, to = c(-.5, .5))
dat$DWilsonWk9MRWeeklyTally0 = rescale(dat$DWilsonWk9MRWeeklyTally0, to = c(-.5, .5))
dat$DWilsonMR29Cumu1 = rescale(dat$DWilsonMR29Cumu1, to = c(-.5, .5))
dat$DWilsonWk9MRWeeklyTally1 = rescale(dat$DWilsonWk9MRWeeklyTally1, to = c(-.5, .5))
dat$DWilsonMR29PB1 = rescale(dat$DWilsonMR29PB1, to = c(-.5, .5))
dat$DWilsonMR29Cumu2 = rescale(dat$DWilsonMR29Cumu2, to = c(-.5, .5))
dat$DWilsonWk9MRWeeklyTally2 = rescale(dat$DWilsonWk9MRWeeklyTally2, to = c(-.5, .5))
dat$DWilsonMR29PB2 = rescale(dat$DWilsonMR29PB2, to = c(-.5, .5))
dat$DWilsonAccAccessedRecogMemAff = rescale(dat$DWilsonAccAccessedRecogMemAff, to = c(-.5, .5))
dat$RJonesMemAff5 = rescale(dat$RJonesMemAff5, to = c(-.5, .5))
dat$RJonesMemAff50 = rescale(dat$RJonesMemAff50, to = c(-.5, .5))
dat$RJonesIWMemAff5 = rescale(dat$RJonesIWMemAff5, to = c(-.5, .5))
dat$RJonesAccRecogMemAff5 = rescale(dat$RJonesAccRecogMemAff5, to = c(-.5, .5))
dat$RJonesDifAff = rescale(dat$RJonesDifAff, to = c(-.5, .5))
dat$RJonesIWDifAff = rescale(dat$RJonesIWDifAff, to = c(-.5, .5))
dat$RJonesMemAff = rescale(dat$RJonesMemAff, to = c(-.5, .5))
dat$RJonesMemAff0 = rescale(dat$RJonesMemAff0, to = c(-.5, .5))
dat$RJonesIWMemAff = rescale(dat$RJonesIWMemAff, to = c(-.5, .5))
dat$RJonesIWMemAff = rescale(dat$RJonesIWMemAff, to = c(-.5, .5))
dat$RJonesAccRecogMemAff10 = rescale(dat$RJonesAccRecogMemAff10, to = c(-.5, .5))
dat$RJones25Cumu0 = rescale(dat$RJones25Cumu0, to = c(-.5, .5))
dat$RJonesWk5WeeklyTally0 = rescale(dat$RJonesWk5WeeklyTally0, to = c(-.5, .5))
dat$RJones25Cumu1 = rescale(dat$RJones25Cumu1, to = c(-.5, .5))
dat$RJonesWk5WeeklyTally1 = rescale(dat$RJonesWk5WeeklyTally1, to = c(-.5, .5))
dat$RJonesWk25WeeklyPBTally1 = rescale(dat$RJonesWk25WeeklyPBTally1, to = c(-.5, .5))
dat$RJonesWk25WeeklyPBTally2 = rescale(dat$RJonesWk25WeeklyPBTally2, to = c(-.5, .5))
dat$RJones25Cumu2 = rescale(dat$RJones25Cumu2, to = c(-.5, .5))
dat$RJonesWk5WeeklyTally2 = rescale(dat$RJonesWk5WeeklyTally2, to = c(-.5, .5))
dat$RJones29Cumu0 = rescale(dat$RJones29Cumu0, to = c(-.5, .5))
dat$RJonesWk9WeeklyTally0 = rescale(dat$RJonesWk9WeeklyTally0, to = c(-.5, .5))
dat$RJones29Cumu1 = rescale(dat$RJones29Cumu1, to = c(-.5, .5))
dat$RJonesWk9WeeklyTally1 = rescale(dat$RJonesWk9WeeklyTally1, to = c(-.5, .5))
dat$RJonesWk29WeeklyPBTally1 = rescale(dat$RJonesWk29WeeklyPBTally1, to = c(-.5, .5))
dat$RJonesWk29WeeklyPBTally2 = rescale(dat$RJonesWk29WeeklyPBTally2, to = c(-.5, .5))
dat$RJones29Cumu2 = rescale(dat$RJones29Cumu2, to = c(-.5, .5))
dat$RJonesWk9WeeklyTally2 = rescale(dat$RJonesWk9WeeklyTally2, to = c(-.5, .5))
dat$RJonesMR29Cumu0 = rescale(dat$RJonesMR29Cumu0, to = c(-.5, .5))
dat$RJonesWk9MRWeeklyTally0 = rescale(dat$RJonesWk9MRWeeklyTally0, to = c(-.5, .5))
dat$RJonesMR29Cumu1 = rescale(dat$RJonesMR29Cumu1, to = c(-.5, .5))
dat$RJonesWk9MRWeeklyTally1 = rescale(dat$RJonesWk9MRWeeklyTally1, to = c(-.5, .5))
dat$RJonesMR29PB1 = rescale(dat$RJonesMR29PB1, to = c(-.5, .5))
dat$RJonesMR29Cumu2 = rescale(dat$RJonesMR29Cumu2, to = c(-.5, .5))
dat$RJonesWk9MRWeeklyTally2 = rescale(dat$RJonesWk9MRWeeklyTally2, to = c(-.5, .5))
dat$RJonesMR29PB2 = rescale(dat$RJonesMR29PB2, to = c(-.5, .5))
dat$RJonesAccAccessedRecogMemAff = rescale(dat$RJonesAccAccessedRecogMemAff, to = c(-.5, .5))
dat$RWilliamsMemAff5 = rescale(dat$RWilliamsMemAff5, to = c(-.5, .5))
dat$RWilliamsMemAff50 = rescale(dat$RWilliamsMemAff50, to = c(-.5, .5))
dat$RWilliamsIWMemAff5 = rescale(dat$RWilliamsIWMemAff5, to = c(-.5, .5))
dat$RWilliamsAccRecogMemAff5 = rescale(dat$RWilliamsAccRecogMemAff5, to = c(-.5, .5))
dat$RWilliamsDifAff = rescale(dat$RWilliamsDifAff, to = c(-.5, .5))
dat$RWilliamsIWDifAff = rescale(dat$RWilliamsIWDifAff, to = c(-.5, .5))
dat$RWilliamsMemAff = rescale(dat$RWilliamsMemAff, to = c(-.5, .5))
dat$RWilliamsMemAff0 = rescale(dat$RWilliamsMemAff0, to = c(-.5, .5))
dat$RWilliamsIWMemAff = rescale(dat$RWilliamsIWMemAff, to = c(-.5, .5))
dat$RWilliamsIWMemAff = rescale(dat$RWilliamsIWMemAff, to = c(-.5, .5))
dat$RWilliamsAccRecogMemAff10 = rescale(dat$RWilliamsAccRecogMemAff10, to = c(-.5, .5))
dat$RWilliams25Cumu0 = rescale(dat$RWilliams25Cumu0, to = c(-.5, .5))
dat$RWilliamsWk5WeeklyTally0 = rescale(dat$RWilliamsWk5WeeklyTally0, to = c(-.5, .5))
dat$RWilliams25Cumu1 = rescale(dat$RWilliams25Cumu1, to = c(-.5, .5))
dat$RWilliamsWk5WeeklyTally1 = rescale(dat$RWilliamsWk5WeeklyTally1, to = c(-.5, .5))
dat$RWilliamsWk25WeeklyPBTally1 = rescale(dat$RWilliamsWk25WeeklyPBTally1, to = c(-.5, .5))
dat$RWilliamsWk25WeeklyPBTally2 = rescale(dat$RWilliamsWk25WeeklyPBTally2, to = c(-.5, .5))
dat$RWilliams25Cumu2 = rescale(dat$RWilliams25Cumu2, to = c(-.5, .5))
dat$RWilliamsWk5WeeklyTally2 = rescale(dat$RWilliamsWk5WeeklyTally2, to = c(-.5, .5))
dat$RWilliams29Cumu0 = rescale(dat$RWilliams29Cumu0, to = c(-.5, .5))
dat$RWilliamsWk9WeeklyTally0 = rescale(dat$RWilliamsWk9WeeklyTally0, to = c(-.5, .5))
dat$RWilliams29Cumu1 = rescale(dat$RWilliams29Cumu1, to = c(-.5, .5))
dat$RWilliamsWk9WeeklyTally1 = rescale(dat$RWilliamsWk9WeeklyTally1, to = c(-.5, .5))
dat$RWilliamsWk29WeeklyPBTally1 = rescale(dat$RWilliamsWk29WeeklyPBTally1, to = c(-.5, .5))
dat$RWilliamsWk29WeeklyPBTally2 = rescale(dat$RWilliamsWk29WeeklyPBTally2, to = c(-.5, .5))
dat$RWilliams29Cumu2 = rescale(dat$RWilliams29Cumu2, to = c(-.5, .5))
dat$RWilliamsWk9WeeklyTally2 = rescale(dat$RWilliamsWk9WeeklyTally2, to = c(-.5, .5))
dat$RWilliamsMR29Cumu0 = rescale(dat$RWilliamsMR29Cumu0, to = c(-.5, .5))
dat$RWilliamsWk9MRWeeklyTally0 = rescale(dat$RWilliamsWk9MRWeeklyTally0, to = c(-.5, .5))
dat$RWilliamsMR29Cumu1 = rescale(dat$RWilliamsMR29Cumu1, to = c(-.5, .5))
dat$RWilliamsWk9MRWeeklyTally1 = rescale(dat$RWilliamsWk9MRWeeklyTally1, to = c(-.5, .5))
dat$RWilliamsMR29PB1 = rescale(dat$RWilliamsMR29PB1, to = c(-.5, .5))
dat$RWilliamsMR29Cumu2 = rescale(dat$RWilliamsMR29Cumu2, to = c(-.5, .5))
dat$RWilliamsWk9MRWeeklyTally2 = rescale(dat$RWilliamsWk9MRWeeklyTally2, to = c(-.5, .5))
dat$RWilliamsMR29PB2 = rescale(dat$RWilliamsMR29PB2, to = c(-.5, .5))
dat$RWilliamsAccAccessedRecogMemAff = rescale(dat$RWilliamsAccAccessedRecogMemAff, to = c(-.5, .5))
# recoding PanelLength (which is a control var.)
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(car)
dat$PanelLength <- recode(dat$PanelLength, "2=1; 1=0")
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
## Define Control Variables for all models.
controls = c("Female", "Age", "YrsEduc", "Black", "Latino", "PolSoph", "LibCon", "PanelLength")

## centering all control variables
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(scales)

dat$Age = rescale(dat$Age, to = c(-.5,.5))
dat$YrsEduc = rescale(dat$YrsEduc, to = c(-.5,.5))
dat$PolSoph = rescale(dat$PolSoph, to = c(-.5,.5))
dat$LibCon = rescale(dat$LibCon, to = c(-.5,.5))
```

##### Dropping Missing Values

```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Function to drop rows with missing values
completeFun <- function(data, desiredCols) {
  completeVec <- complete.cases(data[, desiredCols])
  return(data[completeVec, ])
}

# Smith
dat.DSmith.vars.used = as.character(c(c(controls),"DSmithMemAff5", "DSmithMemAff50", "DSmithIWMemAff5", "DSmithAccRecogMemAff5", "DSmithDifAff", "DSmithIWDifAff", "DSmithMemAff", "DSmithMemAff0", "DSmithIWMemAff", "DSmithIWMemAff", "DSmithAccRecogMemAff10", "DSmith25Cumu0", "DSmithWk5WeeklyTally0", "DSmith25Cumu1", "DSmithWk5WeeklyTally1", "DSmithWk25WeeklyPBTally1", "DSmithWk25WeeklyPBTally2", "DSmith25Cumu2", "DSmithWk5WeeklyTally2", "DSmith29Cumu0", "DSmithWk9WeeklyTally0", "DSmith29Cumu1", "DSmithWk9WeeklyTally1", "DSmithWk29WeeklyPBTally1", "DSmithWk29WeeklyPBTally2", "DSmith29Cumu2", "DSmithWk9WeeklyTally2", "DSmithMR29Cumu0", "DSmithWk9MRWeeklyTally0", "DSmithMR29Cumu1", "DSmithWk9MRWeeklyTally1", "DSmithMR29PB1", "DSmithMR29Cumu2", "DSmithWk9MRWeeklyTally2", "DSmithMR29PB2", "DSmithAccAccessedRecogMemAff"))
dat.DSmith = completeFun(dat, dat.DSmith.vars.used)

# Wilson
dat.DWilson.vars.used = as.character(c(c(controls),"DWilsonMemAff5", "DWilsonMemAff50", "DWilsonIWMemAff5", "DWilsonAccRecogMemAff5", "DWilsonDifAff", "DWilsonIWDifAff", "DWilsonMemAff", "DWilsonMemAff0", "DWilsonIWMemAff", "DWilsonIWMemAff", "DWilsonAccRecogMemAff10", "DWilson25Cumu0", "DWilsonWk5WeeklyTally0", "DWilson25Cumu1", "DWilsonWk5WeeklyTally1", "DWilsonWk25WeeklyPBTally1", "DWilsonWk25WeeklyPBTally2", "DWilson25Cumu2", "DWilsonWk5WeeklyTally2", "DWilson29Cumu0", "DWilsonWk9WeeklyTally0", "DWilson29Cumu1", "DWilsonWk9WeeklyTally1", "DWilsonWk29WeeklyPBTally1", "DWilsonWk29WeeklyPBTally2", "DWilson29Cumu2", "DWilsonWk9WeeklyTally2", "DWilsonMR29Cumu0", "DWilsonWk9MRWeeklyTally0", "DWilsonMR29Cumu1", "DWilsonWk9MRWeeklyTally1", "DWilsonMR29PB1", "DWilsonMR29Cumu2", "DWilsonWk9MRWeeklyTally2", "DWilsonMR29PB2", "DWilsonAccAccessedRecogMemAff"))
dat.DWilson = completeFun(dat, dat.DWilson.vars.used)

# Jones
dat.RJones.vars.used = as.character(c(c(controls),"RJonesMemAff5", "RJonesMemAff50", "RJonesIWMemAff5", "RJonesAccRecogMemAff5", "RJonesDifAff", "RJonesIWDifAff", "RJonesMemAff", "RJonesMemAff0", "RJonesIWMemAff", "RJonesIWMemAff", "RJonesAccRecogMemAff10", "RJones25Cumu0", "RJonesWk5WeeklyTally0", "RJones25Cumu1", "RJonesWk5WeeklyTally1", "RJonesWk25WeeklyPBTally1", "RJonesWk25WeeklyPBTally2", "RJones25Cumu2", "RJonesWk5WeeklyTally2", "RJones29Cumu0", "RJonesWk9WeeklyTally0", "RJones29Cumu1", "RJonesWk9WeeklyTally1", "RJonesWk29WeeklyPBTally1", "RJonesWk29WeeklyPBTally2", "RJones29Cumu2", "RJonesWk9WeeklyTally2", "RJonesMR29Cumu0", "RJonesWk9MRWeeklyTally0", "RJonesMR29Cumu1", "RJonesWk9MRWeeklyTally1", "RJonesMR29PB1", "RJonesMR29Cumu2", "RJonesWk9MRWeeklyTally2", "RJonesMR29PB2", "RJonesAccAccessedRecogMemAff"))
dat.RJones = completeFun(dat, dat.RJones.vars.used)


# Williams
dat.RWilliams.vars.used = as.character(c(c(controls),"RWilliamsMemAff5", "RWilliamsMemAff50", "RWilliamsIWMemAff5", "RWilliamsAccRecogMemAff5", "RWilliamsDifAff", "RWilliamsIWDifAff", "RWilliamsMemAff", "RWilliamsMemAff0", "RWilliamsIWMemAff", "RWilliamsIWMemAff", "RWilliamsAccRecogMemAff10", "RWilliams25Cumu0", "RWilliamsWk5WeeklyTally0", "RWilliams25Cumu1", "RWilliamsWk5WeeklyTally1", "RWilliamsWk25WeeklyPBTally1", "RWilliamsWk25WeeklyPBTally2", "RWilliams25Cumu2", "RWilliamsWk5WeeklyTally2", "RWilliams29Cumu0", "RWilliamsWk9WeeklyTally0", "RWilliams29Cumu1", "RWilliamsWk9WeeklyTally1", "RWilliamsWk29WeeklyPBTally1", "RWilliamsWk29WeeklyPBTally2", "RWilliams29Cumu2", "RWilliamsWk9WeeklyTally2", "RWilliamsMR29Cumu0", "RWilliamsWk9MRWeeklyTally0", "RWilliamsMR29Cumu1", "RWilliamsWk9MRWeeklyTally1", "RWilliamsMR29PB1", "RWilliamsMR29Cumu2", "RWilliamsWk9MRWeeklyTally2", "RWilliamsMR29PB2", "RWilliamsAccAccessedRecogMemAff"))
dat.RWilliams = completeFun(dat, dat.RWilliams.vars.used)
```

###### Report of NA's 
- Missing values and total variables (including controls) used in Smith analyses:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(sapply(dat.DSmith.vars.used, function(x) sum(is.na(x))))
```

- Missing values and total variables (including controls) used in Wilson analyses:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(sapply(dat.DWilson.vars.used, function(x) sum(is.na(x))))
```

- Missing values and total variables (including controls) used in Jones analyses:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(sapply(dat.RJones.vars.used, function(x) sum(is.na(x))))
```

- Missing values and total variables (including controls) used in Williams analyses:
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table(sapply(dat.RWilliams.vars.used, function(x) sum(is.na(x))))
```

# HERE
# Only Students Analyses

# Results: Smith Models


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Smith Models
# Table 1
c8.tab.1.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m1.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m2.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithMemAff50"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m3.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithIWMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m4.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithAccRecogMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)

dv.table.1.Smith = colnames(c8.tab.1.Smith$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Smith Models
# Table 2
c8.tab.2.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m5.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m6.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithIWDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m7.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m8.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMemAff0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m9.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithIWMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m10.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithAccRecogMemAff10"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
m11.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithAccAccessedRecogMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)

dv.table.2.Smith = colnames(c8.tab.2.Smith$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Smith Models
# Table 3
c8.tab.3.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t1.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmith25Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t5.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithWk5WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t10.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmith25Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t14.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithWk5WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t15.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithWk25WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t18.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithWk25WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t21.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmith25Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t25.Smith = lm(as.formula(paste("Wk5DemSmithFTR", paste(paste(c(controls, "DSmithWk5WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)

dv.table.3.Smith = colnames(c8.tab.3.Smith$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Smith Models
# Table 4
c8.tab.4.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t31.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmith29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t35.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t40.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmith29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t44.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t45.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk29WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t48.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk29WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t51.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmith29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t55.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)

dv.table.4.Smith = colnames(c8.tab.4.Smith$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Smith Models
# Table 5
c8.tab.5.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t61.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMR29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t65.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9MRWeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t71.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMR29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t75.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9MRWeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t76.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMR29PB1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t81.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMR29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t85.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithWk9MRWeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)
t86.Smith = lm(as.formula(paste("Wk10DemSmithFTR", paste(paste(c(controls, "DSmithMR29PB2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DSmith)

dv.table.5.Smith = colnames(c8.tab.5.Smith$model)[1] # name of the DV
```



## Table 1
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 1
htmlreg(list(c8.tab.1.Smith, m1.Smith, m2.Smith, m3.Smith, m4.Smith),
        label = "tab:1:Smith",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.1.Smith)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 2
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 2
htmlreg(list(c8.tab.2.Smith, m5.Smith, m6.Smith, m7.Smith, m8.Smith, m9.Smith, m10.Smith, m11.Smith),
        label = "tab:2:Smith",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.2.Smith)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```



## Table 3
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 3
htmlreg(list(c8.tab.3.Smith, t1.Smith, t5.Smith, t10.Smith, t14.Smith, t15.Smith, t18.Smith, t21.Smith, t25.Smith),
        label = "tab:3:Smith",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.3.Smith)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 4
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 4
htmlreg(list(c8.tab.4.Smith, t31.Smith, t35.Smith, t40.Smith, t44.Smith, t45.Smith, t48.Smith, t51.Smith, t55.Smith),
        label = "tab:4:Smith",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.4.Smith)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 5
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 5
htmlreg(list(c8.tab.5.Smith, t61.Smith, t65.Smith, t71.Smith, t75.Smith, t76.Smith, t81.Smith, t85.Smith, t86.Smith),
        label = "tab:5:Smith",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.5.Smith)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Effect Sizes
```{r , message=FALSE, warning=FALSE, echo=FALSE}
# computing d equivalents

## Table 1
m1.Smith.d.eq = 2*as.data.frame(summary(m1.Smith)[4])[10,3]/sqrt(m1.Smith$df.residual)
m2.Smith.d.eq = 2*as.data.frame(summary(m2.Smith)[4])[10,3]/sqrt(m2.Smith$df.residual)
m3.Smith.d.eq = 2*as.data.frame(summary(m3.Smith)[4])[10,3]/sqrt(m3.Smith$df.residual)
m4.Smith.d.eq = 2*as.data.frame(summary(m4.Smith)[4])[10,3]/sqrt(m4.Smith$df.residual)

## Table 2
m5.Smith.d.eq = 2*as.data.frame(summary(m5.Smith)[4])[10,3]/sqrt(m5.Smith$df.residual)
m6.Smith.d.eq = 2*as.data.frame(summary(m6.Smith)[4])[10,3]/sqrt(m6.Smith$df.residual)
m7.Smith.d.eq = 2*as.data.frame(summary(m7.Smith)[4])[10,3]/sqrt(m7.Smith$df.residual)
m8.Smith.d.eq = 2*as.data.frame(summary(m8.Smith)[4])[10,3]/sqrt(m8.Smith$df.residual)
m9.Smith.d.eq = 2*as.data.frame(summary(m9.Smith)[4])[10,3]/sqrt(m9.Smith$df.residual)
m10.Smith.d.eq = 2*as.data.frame(summary(m10.Smith)[4])[10,3]/sqrt(m10.Smith$df.residual)
m11.Smith.d.eq = 2*as.data.frame(summary(m11.Smith)[4])[10,3]/sqrt(m11.Smith$df.residual)


## Table 3
t1.Smith.d.eq = 2*as.data.frame(summary(t1.Smith)[4])[10,3]/sqrt(t1.Smith$df.residual)
t5.Smith.d.eq = 2*as.data.frame(summary(t5.Smith)[4])[10,3]/sqrt(t5.Smith$df.residual)
t10.Smith.d.eq = 2*as.data.frame(summary(t10.Smith)[4])[10,3]/sqrt(t10.Smith$df.residual)
t14.Smith.d.eq = 2*as.data.frame(summary(t14.Smith)[4])[10,3]/sqrt(t14.Smith$df.residual)
t15.Smith.d.eq = 2*as.data.frame(summary(t15.Smith)[4])[10,3]/sqrt(t15.Smith$df.residual)
t18.Smith.d.eq = 2*as.data.frame(summary(t18.Smith)[4])[10,3]/sqrt(t18.Smith$df.residual)
t21.Smith.d.eq = 2*as.data.frame(summary(t21.Smith)[4])[10,3]/sqrt(t21.Smith$df.residual)
t25.Smith.d.eq = 2*as.data.frame(summary(t25.Smith)[4])[10,3]/sqrt(t25.Smith$df.residual)

## Table 4
t31.Smith.d.eq = 2*as.data.frame(summary(t31.Smith)[4])[10,3]/sqrt(t31.Smith$df.residual)
t35.Smith.d.eq = 2*as.data.frame(summary(t35.Smith)[4])[10,3]/sqrt(t35.Smith$df.residual)
t40.Smith.d.eq = 2*as.data.frame(summary(t40.Smith)[4])[10,3]/sqrt(t40.Smith$df.residual)
t44.Smith.d.eq = 2*as.data.frame(summary(t44.Smith)[4])[10,3]/sqrt(t44.Smith$df.residual)
t45.Smith.d.eq = 2*as.data.frame(summary(t45.Smith)[4])[10,3]/sqrt(t45.Smith$df.residual)
t48.Smith.d.eq = 2*as.data.frame(summary(t48.Smith)[4])[10,3]/sqrt(t48.Smith$df.residual)
t51.Smith.d.eq = 2*as.data.frame(summary(t51.Smith)[4])[10,3]/sqrt(t51.Smith$df.residual)
t55.Smith.d.eq = 2*as.data.frame(summary(t55.Smith)[4])[10,3]/sqrt(t55.Smith$df.residual)


## Table 5
t61.Smith.d.eq = 2*as.data.frame(summary(t61.Smith)[4])[10,3]/sqrt(t61.Smith$df.residual)
t65.Smith.d.eq = 2*as.data.frame(summary(t65.Smith)[4])[10,3]/sqrt(t65.Smith$df.residual)
t71.Smith.d.eq = 2*as.data.frame(summary(t71.Smith)[4])[10,3]/sqrt(t71.Smith$df.residual)
t75.Smith.d.eq = 2*as.data.frame(summary(t75.Smith)[4])[10,3]/sqrt(t75.Smith$df.residual)
t76.Smith.d.eq = 2*as.data.frame(summary(t76.Smith)[4])[10,3]/sqrt(t76.Smith$df.residual)
t81.Smith.d.eq = 2*as.data.frame(summary(t81.Smith)[4])[10,3]/sqrt(t81.Smith$df.residual)
t85.Smith.d.eq = 2*as.data.frame(summary(t85.Smith)[4])[10,3]/sqrt(t85.Smith$df.residual)
t86.Smith.d.eq = 2*as.data.frame(summary(t86.Smith)[4])[10,3]/sqrt(t86.Smith$df.residual)

if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(lattice)

data.p.Smith = data.frame(
        x = c("m1.Smith", "m2.Smith", "m3.Smith", "m4.Smith", "m5.Smith", "m6.Smith", "m7.Smith", "m8.Smith", "m9.Smith", "m10.Smith", "m11.Smith", "t1.Smith", "t5.Smith", "t10.Smith", "t14.Smith", "t15.Smith", "t18.Smith", "t21.Smith", "t25.Smith", "t31.Smith", "t35.Smith", "t40.Smith", "t44.Smith", "t45.Smith", "t48.Smith", "t51.Smith", "t55.Smith", "t61.Smith", "t65.Smith", "t71.Smith", "t75.Smith", "t76.Smith", "t81.Smith", "t85.Smith", "t86.Smith"),
  dequivalent = c(m1.Smith.d.eq, m2.Smith.d.eq, m3.Smith.d.eq, m4.Smith.d.eq, m5.Smith.d.eq, m6.Smith.d.eq, m7.Smith.d.eq, m8.Smith.d.eq, m9.Smith.d.eq, m10.Smith.d.eq, m11.Smith.d.eq, t1.Smith.d.eq, t5.Smith.d.eq, t10.Smith.d.eq, t14.Smith.d.eq, t15.Smith.d.eq, t18.Smith.d.eq, t21.Smith.d.eq, t25.Smith.d.eq, t31.Smith.d.eq, t35.Smith.d.eq, t40.Smith.d.eq, t44.Smith.d.eq, t45.Smith.d.eq, t48.Smith.d.eq, t51.Smith.d.eq, t55.Smith.d.eq, t61.Smith.d.eq, t65.Smith.d.eq, t71.Smith.d.eq, t75.Smith.d.eq, t76.Smith.d.eq, t81.Smith.d.eq, t85.Smith.d.eq,t86.Smith.d.eq),
  Candidate= c(rep("Smith", length(dat.DSmith.vars.used)-length(controls)-1))
  )
```


```{r, echo = FALSE, fig.pos='h', warning = FALSE, message = F, fig.width=13, fig.height=6}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(ggplot2)

ggplot() + 
        geom_point(data=data.p.Smith, mapping=aes(x=x, y = dequivalent)) + 
        theme_bw() + 
        scale_x_discrete(name='Model', labels = c(gsub(".Smith", "", as.character(levels(data.p.Smith$x))))) +
        scale_y_continuous(name='D-Equivalent Statistic: Smith') +
        geom_hline(yintercept=0,  linetype="dashed", color = "red", size=1)
```


# Results: Wilson Models

```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Wilson Models
# Table 1
c8.tab.1.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m1.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m2.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonMemAff50"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m3.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonIWMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m4.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonAccRecogMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)

dv.table.1.Wilson = colnames(c8.tab.1.Wilson$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Wilson Models
# Table 2
c8.tab.2.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m5.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m6.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonIWDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m7.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m8.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMemAff0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m9.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonIWMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m10.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonAccRecogMemAff10"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
m11.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonAccAccessedRecogMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)

dv.table.2.Wilson = colnames(c8.tab.2.Wilson$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Wilson Models
# Table 3
c8.tab.3.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t1.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilson25Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t5.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonWk5WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t10.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilson25Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t14.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonWk5WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t15.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonWk25WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t18.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonWk25WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t21.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilson25Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t25.Wilson = lm(as.formula(paste("Wk5DemWilsonFTR", paste(paste(c(controls, "DWilsonWk5WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)

dv.table.3.Wilson = colnames(c8.tab.3.Wilson$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Wilson Models
# Table 4
c8.tab.4.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t31.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilson29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t35.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t40.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilson29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t44.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t45.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk29WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t48.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk29WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t51.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilson29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t55.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)

dv.table.4.Wilson = colnames(c8.tab.4.Wilson$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Wilson Models
# Table 5
c8.tab.5.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t61.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMR29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t65.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9MRWeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t71.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMR29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t75.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9MRWeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t76.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMR29PB1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t81.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMR29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t85.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonWk9MRWeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)
t86.Wilson = lm(as.formula(paste("Wk10DemWilsonFTR", paste(paste(c(controls, "DWilsonMR29PB2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.DWilson)

dv.table.5.Wilson = colnames(c8.tab.5.Wilson$model)[1] # name of the DV
```



## Table 1
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 1
htmlreg(list(c8.tab.1.Wilson, m1.Wilson, m2.Wilson, m3.Wilson, m4.Wilson),
        label = "tab:1:Wilson",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.1.Wilson)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 2
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 2
htmlreg(list(c8.tab.2.Wilson, m5.Wilson, m6.Wilson, m7.Wilson, m8.Wilson, m9.Wilson, m10.Wilson, m11.Wilson),
        label = "tab:2:Wilson",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.2.Wilson)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```



## Table 3
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 3
htmlreg(list(c8.tab.3.Wilson, t1.Wilson, t5.Wilson, t10.Wilson, t14.Wilson, t15.Wilson, t18.Wilson, t21.Wilson, t25.Wilson),
        label = "tab:3:Wilson",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.3.Wilson)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


### Table 4
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 4
htmlreg(list(c8.tab.4.Wilson, t31.Wilson, t35.Wilson, t40.Wilson, t44.Wilson, t45.Wilson, t48.Wilson, t51.Wilson, t55.Wilson),
        label = "tab:4:Wilson",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.4.Wilson)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 5
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 5
htmlreg(list(c8.tab.5.Wilson, t61.Wilson, t65.Wilson, t71.Wilson, t75.Wilson, t76.Wilson, t81.Wilson, t85.Wilson, t86.Wilson),
        label = "tab:5:Wilson",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.5.Wilson)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Effect Sizes
```{r , message=FALSE, warning=FALSE, echo=FALSE}
# computing d equivalents

## Table 1
m1.Wilson.d.eq = 2*as.data.frame(summary(m1.Wilson)[4])[10,3]/sqrt(m1.Wilson$df.residual)
m2.Wilson.d.eq = 2*as.data.frame(summary(m2.Wilson)[4])[10,3]/sqrt(m2.Wilson$df.residual)
m3.Wilson.d.eq = 2*as.data.frame(summary(m3.Wilson)[4])[10,3]/sqrt(m3.Wilson$df.residual)
m4.Wilson.d.eq = 2*as.data.frame(summary(m4.Wilson)[4])[10,3]/sqrt(m4.Wilson$df.residual)

## Table 2
m5.Wilson.d.eq = 2*as.data.frame(summary(m5.Wilson)[4])[10,3]/sqrt(m5.Wilson$df.residual)
m6.Wilson.d.eq = 2*as.data.frame(summary(m6.Wilson)[4])[10,3]/sqrt(m6.Wilson$df.residual)
m7.Wilson.d.eq = 2*as.data.frame(summary(m7.Wilson)[4])[10,3]/sqrt(m7.Wilson$df.residual)
m8.Wilson.d.eq = 2*as.data.frame(summary(m8.Wilson)[4])[10,3]/sqrt(m8.Wilson$df.residual)
m9.Wilson.d.eq = 2*as.data.frame(summary(m9.Wilson)[4])[10,3]/sqrt(m9.Wilson$df.residual)
m10.Wilson.d.eq = 2*as.data.frame(summary(m10.Wilson)[4])[10,3]/sqrt(m10.Wilson$df.residual)
m11.Wilson.d.eq = 2*as.data.frame(summary(m11.Wilson)[4])[10,3]/sqrt(m11.Wilson$df.residual)


## Table 3
t1.Wilson.d.eq = 2*as.data.frame(summary(t1.Wilson)[4])[10,3]/sqrt(t1.Wilson$df.residual)
t5.Wilson.d.eq = 2*as.data.frame(summary(t5.Wilson)[4])[10,3]/sqrt(t5.Wilson$df.residual)
t10.Wilson.d.eq = 2*as.data.frame(summary(t10.Wilson)[4])[10,3]/sqrt(t10.Wilson$df.residual)
t14.Wilson.d.eq = 2*as.data.frame(summary(t14.Wilson)[4])[10,3]/sqrt(t14.Wilson$df.residual)
t15.Wilson.d.eq = 2*as.data.frame(summary(t15.Wilson)[4])[10,3]/sqrt(t15.Wilson$df.residual)
t18.Wilson.d.eq = 2*as.data.frame(summary(t18.Wilson)[4])[10,3]/sqrt(t18.Wilson$df.residual)
t21.Wilson.d.eq = 2*as.data.frame(summary(t21.Wilson)[4])[10,3]/sqrt(t21.Wilson$df.residual)
t25.Wilson.d.eq = 2*as.data.frame(summary(t25.Wilson)[4])[10,3]/sqrt(t25.Wilson$df.residual)

## Table 4
t31.Wilson.d.eq = 2*as.data.frame(summary(t31.Wilson)[4])[10,3]/sqrt(t31.Wilson$df.residual)
t35.Wilson.d.eq = 2*as.data.frame(summary(t35.Wilson)[4])[10,3]/sqrt(t35.Wilson$df.residual)
t40.Wilson.d.eq = 2*as.data.frame(summary(t40.Wilson)[4])[10,3]/sqrt(t40.Wilson$df.residual)
t44.Wilson.d.eq = 2*as.data.frame(summary(t44.Wilson)[4])[10,3]/sqrt(t44.Wilson$df.residual)
t45.Wilson.d.eq = 2*as.data.frame(summary(t45.Wilson)[4])[10,3]/sqrt(t45.Wilson$df.residual)
t48.Wilson.d.eq = 2*as.data.frame(summary(t48.Wilson)[4])[10,3]/sqrt(t48.Wilson$df.residual)
t51.Wilson.d.eq = 2*as.data.frame(summary(t51.Wilson)[4])[10,3]/sqrt(t51.Wilson$df.residual)
t55.Wilson.d.eq = 2*as.data.frame(summary(t55.Wilson)[4])[10,3]/sqrt(t55.Wilson$df.residual)


## Table 5
t61.Wilson.d.eq = 2*as.data.frame(summary(t61.Wilson)[4])[10,3]/sqrt(t61.Wilson$df.residual)
t65.Wilson.d.eq = 2*as.data.frame(summary(t65.Wilson)[4])[10,3]/sqrt(t65.Wilson$df.residual)
t71.Wilson.d.eq = 2*as.data.frame(summary(t71.Wilson)[4])[10,3]/sqrt(t71.Wilson$df.residual)
t75.Wilson.d.eq = 2*as.data.frame(summary(t75.Wilson)[4])[10,3]/sqrt(t75.Wilson$df.residual)
t76.Wilson.d.eq = 2*as.data.frame(summary(t76.Wilson)[4])[10,3]/sqrt(t76.Wilson$df.residual)
t81.Wilson.d.eq = 2*as.data.frame(summary(t81.Wilson)[4])[10,3]/sqrt(t81.Wilson$df.residual)
t85.Wilson.d.eq = 2*as.data.frame(summary(t85.Wilson)[4])[10,3]/sqrt(t85.Wilson$df.residual)
t86.Wilson.d.eq = 2*as.data.frame(summary(t86.Wilson)[4])[10,3]/sqrt(t86.Wilson$df.residual)

if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(lattice)

data.p.Wilson = data.frame(
        x = c("m1.Wilson", "m2.Wilson", "m3.Wilson", "m4.Wilson", "m5.Wilson", "m6.Wilson", "m7.Wilson", "m8.Wilson", "m9.Wilson", "m10.Wilson", "m11.Wilson", "t1.Wilson", "t5.Wilson", "t10.Wilson", "t14.Wilson", "t15.Wilson", "t18.Wilson", "t21.Wilson", "t25.Wilson", "t31.Wilson", "t35.Wilson", "t40.Wilson", "t44.Wilson", "t45.Wilson", "t48.Wilson", "t51.Wilson", "t55.Wilson", "t61.Wilson", "t65.Wilson", "t71.Wilson", "t75.Wilson", "t76.Wilson", "t81.Wilson", "t85.Wilson", "t86.Wilson"),
  dequivalent = c(m1.Wilson.d.eq, m2.Wilson.d.eq, m3.Wilson.d.eq, m4.Wilson.d.eq, m5.Wilson.d.eq, m6.Wilson.d.eq, m7.Wilson.d.eq, m8.Wilson.d.eq, m9.Wilson.d.eq, m10.Wilson.d.eq, m11.Wilson.d.eq, t1.Wilson.d.eq, t5.Wilson.d.eq, t10.Wilson.d.eq, t14.Wilson.d.eq, t15.Wilson.d.eq, t18.Wilson.d.eq, t21.Wilson.d.eq, t25.Wilson.d.eq, t31.Wilson.d.eq, t35.Wilson.d.eq, t40.Wilson.d.eq, t44.Wilson.d.eq, t45.Wilson.d.eq, t48.Wilson.d.eq, t51.Wilson.d.eq, t55.Wilson.d.eq, t61.Wilson.d.eq, t65.Wilson.d.eq, t71.Wilson.d.eq, t75.Wilson.d.eq, t76.Wilson.d.eq, t81.Wilson.d.eq, t85.Wilson.d.eq,t86.Wilson.d.eq),
  Candidate= c(rep("Wilson", length(dat.DWilson.vars.used)-length(controls)-1))
  )
```


```{r, echo = FALSE, fig.pos='h', warning = FALSE, message = F, fig.width=13, fig.height=6}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(ggplot2)

ggplot() + 
        geom_point(data=data.p.Wilson, mapping=aes(x=x, y = dequivalent)) + 
        theme_bw() + 
        scale_x_discrete(name='Model', labels = c(gsub(".Wilson", "", as.character(levels(data.p.Wilson$x))))) +
        scale_y_continuous(name='D-Equivalent Statistic: Wilson') +
        geom_hline(yintercept=0,  linetype="dashed", color = "red", size=1)
```


# Results: Jones Models


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Jones Models
# Table 1
c8.tab.1.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RJones)
m1.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m2.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesMemAff50"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m3.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesIWMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m4.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesAccRecogMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)

dv.table.1.Jones = colnames(c8.tab.1.Jones$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Jones Models
# Table 2
c8.tab.2.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RJones)
m5.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m6.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesIWDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m7.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m8.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMemAff0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m9.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesIWMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m10.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesAccRecogMemAff10"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
m11.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesAccAccessedRecogMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)

dv.table.2.Jones = colnames(c8.tab.2.Jones$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Jones Models
# Table 3
c8.tab.3.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RJones)
t1.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJones25Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t5.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesWk5WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t10.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJones25Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t14.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesWk5WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t15.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesWk25WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t18.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesWk25WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t21.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJones25Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t25.Jones = lm(as.formula(paste("Wk5RepJonesFTR", paste(paste(c(controls, "RJonesWk5WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)

dv.table.3.Jones = colnames(c8.tab.3.Jones$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Jones Models
# Table 4
c8.tab.4.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RJones)
t31.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJones29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t35.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t40.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJones29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t44.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t45.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk29WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t48.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk29WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t51.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJones29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t55.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)

dv.table.4.Jones = colnames(c8.tab.4.Jones$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Jones Models
# Table 5
c8.tab.5.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RJones)
t61.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMR29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t65.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9MRWeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t71.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMR29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t75.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9MRWeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t76.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMR29PB1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t81.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMR29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t85.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesWk9MRWeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)
t86.Jones = lm(as.formula(paste("Wk10RepJonesFTR", paste(paste(c(controls, "RJonesMR29PB2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RJones)

dv.table.5.Jones = colnames(c8.tab.5.Jones$model)[1] # name of the DV
```



## Table 1
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 1
htmlreg(list(c8.tab.1.Jones, m1.Jones, m2.Jones, m3.Jones, m4.Jones),
        label = "tab:1:Jones",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.1.Jones)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 2
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 2
htmlreg(list(c8.tab.2.Jones, m5.Jones, m6.Jones, m7.Jones, m8.Jones, m9.Jones, m10.Jones, m11.Jones),
        label = "tab:2:Jones",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.2.Jones)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```



## Table 3
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 3
htmlreg(list(c8.tab.3.Jones, t1.Jones, t5.Jones, t10.Jones, t14.Jones, t15.Jones, t18.Jones, t21.Jones, t25.Jones),
        label = "tab:3:Jones",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.3.Jones)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 4
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 4
htmlreg(list(c8.tab.4.Jones, t31.Jones, t35.Jones, t40.Jones, t44.Jones, t45.Jones, t48.Jones, t51.Jones, t55.Jones),
        label = "tab:4:Jones",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.4.Jones)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 5
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 5
htmlreg(list(c8.tab.5.Jones, t61.Jones, t65.Jones, t71.Jones, t75.Jones, t76.Jones, t81.Jones, t85.Jones, t86.Jones),
        label = "tab:5:Jones",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.5.Jones)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Effect Sizes
```{r , message=FALSE, warning=FALSE, echo=FALSE}

# computing d equivalents

## Table 1
m1.Jones.d.eq = 2*as.data.frame(summary(m1.Jones)[4])[10,3]/sqrt(m1.Jones$df.residual)
m2.Jones.d.eq = 2*as.data.frame(summary(m2.Jones)[4])[10,3]/sqrt(m2.Jones$df.residual)
m3.Jones.d.eq = 2*as.data.frame(summary(m3.Jones)[4])[10,3]/sqrt(m3.Jones$df.residual)
m4.Jones.d.eq = 2*as.data.frame(summary(m4.Jones)[4])[10,3]/sqrt(m4.Jones$df.residual)

## Table 2
m5.Jones.d.eq = 2*as.data.frame(summary(m5.Jones)[4])[10,3]/sqrt(m5.Jones$df.residual)
m6.Jones.d.eq = 2*as.data.frame(summary(m6.Jones)[4])[10,3]/sqrt(m6.Jones$df.residual)
m7.Jones.d.eq = 2*as.data.frame(summary(m7.Jones)[4])[10,3]/sqrt(m7.Jones$df.residual)
m8.Jones.d.eq = 2*as.data.frame(summary(m8.Jones)[4])[10,3]/sqrt(m8.Jones$df.residual)
m9.Jones.d.eq = 2*as.data.frame(summary(m9.Jones)[4])[10,3]/sqrt(m9.Jones$df.residual)
m10.Jones.d.eq = 2*as.data.frame(summary(m10.Jones)[4])[10,3]/sqrt(m10.Jones$df.residual)
m11.Jones.d.eq = 2*as.data.frame(summary(m11.Jones)[4])[10,3]/sqrt(m11.Jones$df.residual)


## Table 3
t1.Jones.d.eq = 2*as.data.frame(summary(t1.Jones)[4])[10,3]/sqrt(t1.Jones$df.residual)
t5.Jones.d.eq = 2*as.data.frame(summary(t5.Jones)[4])[10,3]/sqrt(t5.Jones$df.residual)
t10.Jones.d.eq = 2*as.data.frame(summary(t10.Jones)[4])[10,3]/sqrt(t10.Jones$df.residual)
t14.Jones.d.eq = 2*as.data.frame(summary(t14.Jones)[4])[10,3]/sqrt(t14.Jones$df.residual)
t15.Jones.d.eq = 2*as.data.frame(summary(t15.Jones)[4])[10,3]/sqrt(t15.Jones$df.residual)
t18.Jones.d.eq = 2*as.data.frame(summary(t18.Jones)[4])[10,3]/sqrt(t18.Jones$df.residual)
t21.Jones.d.eq = 2*as.data.frame(summary(t21.Jones)[4])[10,3]/sqrt(t21.Jones$df.residual)
t25.Jones.d.eq = 2*as.data.frame(summary(t25.Jones)[4])[10,3]/sqrt(t25.Jones$df.residual)

## Table 4
t31.Jones.d.eq = 2*as.data.frame(summary(t31.Jones)[4])[10,3]/sqrt(t31.Jones$df.residual)
t35.Jones.d.eq = 2*as.data.frame(summary(t35.Jones)[4])[10,3]/sqrt(t35.Jones$df.residual)
t40.Jones.d.eq = 2*as.data.frame(summary(t40.Jones)[4])[10,3]/sqrt(t40.Jones$df.residual)
t44.Jones.d.eq = 2*as.data.frame(summary(t44.Jones)[4])[10,3]/sqrt(t44.Jones$df.residual)
t45.Jones.d.eq = 2*as.data.frame(summary(t45.Jones)[4])[10,3]/sqrt(t45.Jones$df.residual)
t48.Jones.d.eq = 2*as.data.frame(summary(t48.Jones)[4])[10,3]/sqrt(t48.Jones$df.residual)
t51.Jones.d.eq = 2*as.data.frame(summary(t51.Jones)[4])[10,3]/sqrt(t51.Jones$df.residual)
t55.Jones.d.eq = 2*as.data.frame(summary(t55.Jones)[4])[10,3]/sqrt(t55.Jones$df.residual)


## Table 5
t61.Jones.d.eq = 2*as.data.frame(summary(t61.Jones)[4])[10,3]/sqrt(t61.Jones$df.residual)
t65.Jones.d.eq = 2*as.data.frame(summary(t65.Jones)[4])[10,3]/sqrt(t65.Jones$df.residual)
t71.Jones.d.eq = 2*as.data.frame(summary(t71.Jones)[4])[10,3]/sqrt(t71.Jones$df.residual)
t75.Jones.d.eq = 2*as.data.frame(summary(t75.Jones)[4])[10,3]/sqrt(t75.Jones$df.residual)
t76.Jones.d.eq = 2*as.data.frame(summary(t76.Jones)[4])[10,3]/sqrt(t76.Jones$df.residual)
t81.Jones.d.eq = 2*as.data.frame(summary(t81.Jones)[4])[10,3]/sqrt(t81.Jones$df.residual)
t85.Jones.d.eq = 2*as.data.frame(summary(t85.Jones)[4])[10,3]/sqrt(t85.Jones$df.residual)
t86.Jones.d.eq = 2*as.data.frame(summary(t86.Jones)[4])[10,3]/sqrt(t86.Jones$df.residual)

if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(lattice)

data.p.Jones = data.frame(
        x = c("m1.Jones", "m2.Jones", "m3.Jones", "m4.Jones", "m5.Jones", "m6.Jones", "m7.Jones", "m8.Jones", "m9.Jones", "m10.Jones", "m11.Jones", "t1.Jones", "t5.Jones", "t10.Jones", "t14.Jones", "t15.Jones", "t18.Jones", "t21.Jones", "t25.Jones", "t31.Jones", "t35.Jones", "t40.Jones", "t44.Jones", "t45.Jones", "t48.Jones", "t51.Jones", "t55.Jones", "t61.Jones", "t65.Jones", "t71.Jones", "t75.Jones", "t76.Jones", "t81.Jones", "t85.Jones", "t86.Jones"),
  dequivalent = c(m1.Jones.d.eq, m2.Jones.d.eq, m3.Jones.d.eq, m4.Jones.d.eq, m5.Jones.d.eq, m6.Jones.d.eq, m7.Jones.d.eq, m8.Jones.d.eq, m9.Jones.d.eq, m10.Jones.d.eq, m11.Jones.d.eq, t1.Jones.d.eq, t5.Jones.d.eq, t10.Jones.d.eq, t14.Jones.d.eq, t15.Jones.d.eq, t18.Jones.d.eq, t21.Jones.d.eq, t25.Jones.d.eq, t31.Jones.d.eq, t35.Jones.d.eq, t40.Jones.d.eq, t44.Jones.d.eq, t45.Jones.d.eq, t48.Jones.d.eq, t51.Jones.d.eq, t55.Jones.d.eq, t61.Jones.d.eq, t65.Jones.d.eq, t71.Jones.d.eq, t75.Jones.d.eq, t76.Jones.d.eq, t81.Jones.d.eq, t85.Jones.d.eq,t86.Jones.d.eq),
  Candidate= c(rep("Jones", length(dat.RJones.vars.used)-length(controls)-1))
  )
```


```{r, echo = FALSE, fig.pos='h', warning = FALSE, message = F, fig.width=13, fig.height=6}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(ggplot2)

ggplot() + 
        geom_point(data=data.p.Jones, mapping=aes(x=x, y = dequivalent)) + 
        theme_bw() + 
        scale_x_discrete(name='Model', labels = c(gsub(".Jones", "", as.character(levels(data.p.Jones$x))))) +
        scale_y_continuous(name='D-Equivalent Statistic: Jones') +
        geom_hline(yintercept=0,  linetype="dashed", color = "red", size=1)
```

# Results: Williams Models


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Williams Models
# Table 1
c8.tab.1.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m1.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m2.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMemAff50"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m3.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsIWMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m4.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsAccRecogMemAff5"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)

dv.table.1.Williams = colnames(c8.tab.1.Williams$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Williams Models
# Table 2
c8.tab.2.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m5.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m6.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsIWDifAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m7.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m8.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMemAff0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m9.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsIWMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m10.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsAccRecogMemAff10"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
m11.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsAccAccessedRecogMemAff"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)

dv.table.2.Williams = colnames(c8.tab.2.Williams$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Williams Models
# Table 3
c8.tab.3.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t1.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliams25Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t5.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk5WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t10.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliams25Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t14.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk5WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t15.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk25WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t18.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk25WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t21.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliams25Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t25.Williams = lm(as.formula(paste("Wk5RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk5WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)

dv.table.3.Williams = colnames(c8.tab.3.Williams$model)[1] # name of the DV
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Williams Models
# Table 4
c8.tab.4.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t31.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliams29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t35.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9WeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t40.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliams29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t44.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9WeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t45.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk29WeeklyPBTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t48.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk29WeeklyPBTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t51.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliams29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t55.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9WeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)

dv.table.4.Williams = colnames(c8.tab.4.Williams$model)[1] # name of the DV
```



```{r , message=FALSE, warning=FALSE, echo=FALSE}
# Williams Models
# Table 5
c8.tab.5.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(controls, collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t61.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMR29Cumu0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t65.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9MRWeeklyTally0"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t71.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMR29Cumu1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t75.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9MRWeeklyTally1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t76.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMR29PB1"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t81.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMR29Cumu2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t85.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsWk9MRWeeklyTally2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)
t86.Williams = lm(as.formula(paste("Wk10RepWilliamsFTR", paste(paste(c(controls, "RWilliamsMR29PB2"), collapse=" + "), collapse=" + "), sep=" ~ ")), data=dat.RWilliams)

dv.table.5.Williams = colnames(c8.tab.5.Williams$model)[1] # name of the DV
```



## Table 1
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 1
htmlreg(list(c8.tab.1.Williams, m1.Williams, m2.Williams, m3.Williams, m4.Williams),
        label = "tab:1:Williams",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.1.Williams)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 2
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 2
htmlreg(list(c8.tab.2.Williams, m5.Williams, m6.Williams, m7.Williams, m8.Williams, m9.Williams, m10.Williams, m11.Williams),
        label = "tab:2:Williams",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.2.Williams)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```



## Table 3
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 3
htmlreg(list(c8.tab.3.Williams, t1.Williams, t5.Williams, t10.Williams, t14.Williams, t15.Williams, t18.Williams, t21.Williams, t25.Williams),
        label = "tab:3:Williams",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.3.Williams)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 4
```{r , message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 4
htmlreg(list(c8.tab.4.Williams, t31.Williams, t35.Williams, t40.Williams, t44.Williams, t45.Williams, t48.Williams, t51.Williams, t55.Williams),
        label = "tab:4:Williams",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.4.Williams)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Table 5
```{r, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(texreg)

# table 5
htmlreg(list(c8.tab.5.Williams, t61.Williams, t65.Williams, t71.Williams, t75.Williams, t76.Williams, t81.Williams, t85.Williams, t86.Williams),
        label = "tab:5:Williams",
        custom.note = list(paste(c("%stars. All models, OLS. DV: "), dv.table.5.Williams)),
        #fontsize = "tiny",
        center = TRUE,
        digits = 3,
        table = TRUE,
        float.pos = "h",
        caption = ""
        )
```


## Effect Sizes
```{r , message=FALSE, warning=FALSE, echo=FALSE}

# computing d equivalents

## Table 1
m1.Williams.d.eq = 2*as.data.frame(summary(m1.Williams)[4])[10,3]/sqrt(m1.Williams$df.residual)
m2.Williams.d.eq = 2*as.data.frame(summary(m2.Williams)[4])[10,3]/sqrt(m2.Williams$df.residual)
m3.Williams.d.eq = 2*as.data.frame(summary(m3.Williams)[4])[10,3]/sqrt(m3.Williams$df.residual)
m4.Williams.d.eq = 2*as.data.frame(summary(m4.Williams)[4])[10,3]/sqrt(m4.Williams$df.residual)

## Table 2
m5.Williams.d.eq = 2*as.data.frame(summary(m5.Williams)[4])[10,3]/sqrt(m5.Williams$df.residual)
m6.Williams.d.eq = 2*as.data.frame(summary(m6.Williams)[4])[10,3]/sqrt(m6.Williams$df.residual)
m7.Williams.d.eq = 2*as.data.frame(summary(m7.Williams)[4])[10,3]/sqrt(m7.Williams$df.residual)
m8.Williams.d.eq = 2*as.data.frame(summary(m8.Williams)[4])[10,3]/sqrt(m8.Williams$df.residual)
m9.Williams.d.eq = 2*as.data.frame(summary(m9.Williams)[4])[10,3]/sqrt(m9.Williams$df.residual)
m10.Williams.d.eq = 2*as.data.frame(summary(m10.Williams)[4])[10,3]/sqrt(m10.Williams$df.residual)
m11.Williams.d.eq = 2*as.data.frame(summary(m11.Williams)[4])[10,3]/sqrt(m11.Williams$df.residual)


## Table 3
t1.Williams.d.eq = 2*as.data.frame(summary(t1.Williams)[4])[10,3]/sqrt(t1.Williams$df.residual)
t5.Williams.d.eq = 2*as.data.frame(summary(t5.Williams)[4])[10,3]/sqrt(t5.Williams$df.residual)
t10.Williams.d.eq = 2*as.data.frame(summary(t10.Williams)[4])[10,3]/sqrt(t10.Williams$df.residual)
t14.Williams.d.eq = 2*as.data.frame(summary(t14.Williams)[4])[10,3]/sqrt(t14.Williams$df.residual)
t15.Williams.d.eq = 2*as.data.frame(summary(t15.Williams)[4])[10,3]/sqrt(t15.Williams$df.residual)
t18.Williams.d.eq = 2*as.data.frame(summary(t18.Williams)[4])[10,3]/sqrt(t18.Williams$df.residual)
t21.Williams.d.eq = 2*as.data.frame(summary(t21.Williams)[4])[10,3]/sqrt(t21.Williams$df.residual)
t25.Williams.d.eq = 2*as.data.frame(summary(t25.Williams)[4])[10,3]/sqrt(t25.Williams$df.residual)

## Table 4
t31.Williams.d.eq = 2*as.data.frame(summary(t31.Williams)[4])[10,3]/sqrt(t31.Williams$df.residual)
t35.Williams.d.eq = 2*as.data.frame(summary(t35.Williams)[4])[10,3]/sqrt(t35.Williams$df.residual)
t40.Williams.d.eq = 2*as.data.frame(summary(t40.Williams)[4])[10,3]/sqrt(t40.Williams$df.residual)
t44.Williams.d.eq = 2*as.data.frame(summary(t44.Williams)[4])[10,3]/sqrt(t44.Williams$df.residual)
t45.Williams.d.eq = 2*as.data.frame(summary(t45.Williams)[4])[10,3]/sqrt(t45.Williams$df.residual)
t48.Williams.d.eq = 2*as.data.frame(summary(t48.Williams)[4])[10,3]/sqrt(t48.Williams$df.residual)
t51.Williams.d.eq = 2*as.data.frame(summary(t51.Williams)[4])[10,3]/sqrt(t51.Williams$df.residual)
t55.Williams.d.eq = 2*as.data.frame(summary(t55.Williams)[4])[10,3]/sqrt(t55.Williams$df.residual)


## Table 5
t61.Williams.d.eq = 2*as.data.frame(summary(t61.Williams)[4])[10,3]/sqrt(t61.Williams$df.residual)
t65.Williams.d.eq = 2*as.data.frame(summary(t65.Williams)[4])[10,3]/sqrt(t65.Williams$df.residual)
t71.Williams.d.eq = 2*as.data.frame(summary(t71.Williams)[4])[10,3]/sqrt(t71.Williams$df.residual)
t75.Williams.d.eq = 2*as.data.frame(summary(t75.Williams)[4])[10,3]/sqrt(t75.Williams$df.residual)
t76.Williams.d.eq = 2*as.data.frame(summary(t76.Williams)[4])[10,3]/sqrt(t76.Williams$df.residual)
t81.Williams.d.eq = 2*as.data.frame(summary(t81.Williams)[4])[10,3]/sqrt(t81.Williams$df.residual)
t85.Williams.d.eq = 2*as.data.frame(summary(t85.Williams)[4])[10,3]/sqrt(t85.Williams$df.residual)
t86.Williams.d.eq = 2*as.data.frame(summary(t86.Williams)[4])[10,3]/sqrt(t86.Williams$df.residual)

if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(lattice)

data.p.Williams = data.frame(
        x = c("m1.Williams", "m2.Williams", "m3.Williams", "m4.Williams", "m5.Williams", "m6.Williams", "m7.Williams", "m8.Williams", "m9.Williams", "m10.Williams", "m11.Williams", "t1.Williams", "t5.Williams", "t10.Williams", "t14.Williams", "t15.Williams", "t18.Williams", "t21.Williams", "t25.Williams", "t31.Williams", "t35.Williams", "t40.Williams", "t44.Williams", "t45.Williams", "t48.Williams", "t51.Williams", "t55.Williams", "t61.Williams", "t65.Williams", "t71.Williams", "t75.Williams", "t76.Williams", "t81.Williams", "t85.Williams", "t86.Williams"),
  dequivalent = c(m1.Williams.d.eq, m2.Williams.d.eq, m3.Williams.d.eq, m4.Williams.d.eq, m5.Williams.d.eq, m6.Williams.d.eq, m7.Williams.d.eq, m8.Williams.d.eq, m9.Williams.d.eq, m10.Williams.d.eq, m11.Williams.d.eq, t1.Williams.d.eq, t5.Williams.d.eq, t10.Williams.d.eq, t14.Williams.d.eq, t15.Williams.d.eq, t18.Williams.d.eq, t21.Williams.d.eq, t25.Williams.d.eq, t31.Williams.d.eq, t35.Williams.d.eq, t40.Williams.d.eq, t44.Williams.d.eq, t45.Williams.d.eq, t48.Williams.d.eq, t51.Williams.d.eq, t55.Williams.d.eq, t61.Williams.d.eq, t65.Williams.d.eq, t71.Williams.d.eq, t75.Williams.d.eq, t76.Williams.d.eq, t81.Williams.d.eq, t85.Williams.d.eq,t86.Williams.d.eq),
  Candidate= c(rep("Williams", length(dat.RWilliams.vars.used)-length(controls)-1))
  )
```


```{r, echo = FALSE, fig.pos='h', warning = FALSE, message = F, fig.width=13, fig.height=6}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(ggplot2)

ggplot() + 
        geom_point(data=data.p.Williams, mapping=aes(x=x, y = dequivalent)) + 
        theme_bw() + 
        scale_x_discrete(name='Model', labels = c(gsub(".Williams", "", as.character(levels(data.p.Williams$x))))) +
        scale_y_continuous(name='D-Equivalent Statistic: Williams') +
        geom_hline(yintercept=0,  linetype="dashed", color = "red", size=1)
```

# Summaries

## Plot: Combined Effect Sizes by Candidate

```{r , message=FALSE, warning=FALSE, echo=FALSE}
Smith.for.plot.combined = as.data.frame(cbind(
  x = c(gsub(".Smith", "", as.character(levels(data.p.Smith$x)))),
  value = data.p.Smith[2],
  candidate = data.p.Smith[3]
  ))

Wilson.for.plot.combined = as.data.frame(cbind(
  x = c(gsub(".Wilson", "", as.character(levels(data.p.Wilson$x)))),
  value = data.p.Wilson[2],
  candidate = data.p.Wilson[3]
  ))

Jones.for.plot.combined = as.data.frame(cbind(
  x = c(gsub(".Jones", "", as.character(levels(data.p.Jones$x)))),
  value = data.p.Jones[2],
  candidate = data.p.Jones[3]
  ))

Williams.for.plot.combined = as.data.frame(cbind(
  x = c(gsub(".Williams", "", as.character(levels(data.p.Williams$x)))),
  value = data.p.Williams[2],
  candidate = data.p.Williams[3]
  ))


effect.sizes.plot.d.combined = as.data.frame(rbind(
  Smith.for.plot.combined,
  Wilson.for.plot.combined,
  Jones.for.plot.combined,
  Williams.for.plot.combined))
```

```{r, echo = FALSE, fig.pos='h', warning = FALSE, message = F, fig.width=13, fig.height=6}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(ggplot2)

ggplot() + 
        geom_point(data=effect.sizes.plot.d.combined, mapping=aes(x=x, y = dequivalent, colour=Candidate)) + 
        theme_bw() + 
        scale_x_discrete(name='Model', labels = c(gsub(".Williams", "", as.character(levels(data.p.Williams$x))))) +
        scale_y_continuous(name='D-Equivalent Statistic') +
        geom_hline(yintercept=0,  linetype="dashed", color = "red", size=1)
```

## Table: Combined Effect Sizes by Variable

```{r , message=FALSE, warning=FALSE, echo=FALSE}
#### Smith #### 
coefficients.Smith.table = data.frame(
  Coefficient = c(
    # Affective Memory: Table 1
    as.data.frame(summary(m1.Smith)[4])[10,1], 
    as.data.frame(summary(m2.Smith)[4])[10,1], 
    as.data.frame(summary(m3.Smith)[4])[10,1], 
    as.data.frame(summary(m4.Smith)[4])[10,1], 
    # Affective Memory: Table 2
    as.data.frame(summary(m5.Smith)[4])[10,1],
    as.data.frame(summary(m6.Smith)[4])[10,1],
    as.data.frame(summary(m7.Smith)[4])[10,1],
    as.data.frame(summary(m8.Smith)[4])[10,1],
    as.data.frame(summary(m9.Smith)[4])[10,1],
    as.data.frame(summary(m10.Smith)[4])[10,1],
    as.data.frame(summary(m11.Smith)[4])[10,1],
    # Table 3: Running Tally
    as.data.frame(summary(t1.Smith)[4])[10,1], 
    as.data.frame(summary(t5.Smith)[4])[10,1], 
    as.data.frame(summary(t10.Smith)[4])[10,1], 
    as.data.frame(summary(t14.Smith)[4])[10,1], 
    as.data.frame(summary(t15.Smith)[4])[10,1], 
    as.data.frame(summary(t18.Smith)[4])[10,1], 
    as.data.frame(summary(t21.Smith)[4])[10,1], 
    as.data.frame(summary(t25.Smith)[4])[10,1], 
    # Table 4: Running Tally
    as.data.frame(summary(t31.Smith)[4])[10,1], 
    as.data.frame(summary(t35.Smith)[4])[10,1], 
    as.data.frame(summary(t40.Smith)[4])[10,1], 
    as.data.frame(summary(t44.Smith)[4])[10,1], 
    as.data.frame(summary(t45.Smith)[4])[10,1], 
    as.data.frame(summary(t48.Smith)[4])[10,1], 
    as.data.frame(summary(t51.Smith)[4])[10,1], 
    as.data.frame(summary(t55.Smith)[4])[10,1], 
    # Table 5: : Running Tally
    as.data.frame(summary(t61.Smith)[4])[10,1],
    as.data.frame(summary(t65.Smith)[4])[10,1],
    as.data.frame(summary(t71.Smith)[4])[10,1],
    as.data.frame(summary(t75.Smith)[4])[10,1],
    as.data.frame(summary(t76.Smith)[4])[10,1],
    as.data.frame(summary(t81.Smith)[4])[10,1],
    as.data.frame(summary(t85.Smith)[4])[10,1],
    as.data.frame(summary(t86.Smith)[4])[10,1]
    ),
  Candidate = rep("Smith",nrow(data.p.Smith)),
  Model = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8", "m9", "m10", "m11", "t1", "t5", "t10", "t14", "t15", "t18", "t21", "t25", "t31", "t35", "t40", "t44", "t45", "t48", "t51", "t55", "t61", "t65", "t71", "t75", "t76", "t81", "t85", "t86")
  )
  
#### Wilson #### 

coefficients.Wilson.table = data.frame(
  Coefficient = c(
    # Affective Memory: Table 1
    as.data.frame(summary(m1.Wilson)[4])[10,1], 
    as.data.frame(summary(m2.Wilson)[4])[10,1], 
    as.data.frame(summary(m3.Wilson)[4])[10,1], 
    as.data.frame(summary(m4.Wilson)[4])[10,1], 
    # Affective Memory: Table 2
    as.data.frame(summary(m5.Wilson)[4])[10,1],
    as.data.frame(summary(m6.Wilson)[4])[10,1],
    as.data.frame(summary(m7.Wilson)[4])[10,1],
    as.data.frame(summary(m8.Wilson)[4])[10,1],
    as.data.frame(summary(m9.Wilson)[4])[10,1],
    as.data.frame(summary(m10.Wilson)[4])[10,1],
    as.data.frame(summary(m11.Wilson)[4])[10,1],
    # Table 3: Running Tally
    as.data.frame(summary(t1.Wilson)[4])[10,1], 
    as.data.frame(summary(t5.Wilson)[4])[10,1], 
    as.data.frame(summary(t10.Wilson)[4])[10,1], 
    as.data.frame(summary(t14.Wilson)[4])[10,1], 
    as.data.frame(summary(t15.Wilson)[4])[10,1], 
    as.data.frame(summary(t18.Wilson)[4])[10,1], 
    as.data.frame(summary(t21.Wilson)[4])[10,1], 
    as.data.frame(summary(t25.Wilson)[4])[10,1], 
    # Table 4: Running Tally
    as.data.frame(summary(t31.Wilson)[4])[10,1], 
    as.data.frame(summary(t35.Wilson)[4])[10,1], 
    as.data.frame(summary(t40.Wilson)[4])[10,1], 
    as.data.frame(summary(t44.Wilson)[4])[10,1], 
    as.data.frame(summary(t45.Wilson)[4])[10,1], 
    as.data.frame(summary(t48.Wilson)[4])[10,1], 
    as.data.frame(summary(t51.Wilson)[4])[10,1], 
    as.data.frame(summary(t55.Wilson)[4])[10,1], 
    # Table 5: : Running Tally
    as.data.frame(summary(t61.Wilson)[4])[10,1],
    as.data.frame(summary(t65.Wilson)[4])[10,1],
    as.data.frame(summary(t71.Wilson)[4])[10,1],
    as.data.frame(summary(t75.Wilson)[4])[10,1],
    as.data.frame(summary(t76.Wilson)[4])[10,1],
    as.data.frame(summary(t81.Wilson)[4])[10,1],
    as.data.frame(summary(t85.Wilson)[4])[10,1],
    as.data.frame(summary(t86.Wilson)[4])[10,1]
    ),
  Candidate = rep("Wilson",nrow(data.p.Wilson)), 
  Model = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8", "m9", "m10", "m11", "t1", "t5", "t10", "t14", "t15", "t18", "t21", "t25", "t31", "t35", "t40", "t44", "t45", "t48", "t51", "t55", "t61", "t65", "t71", "t75", "t76", "t81", "t85", "t86")
  )


#### Jones #### 
coefficients.Jones.table = data.frame(
  Coefficient = c(
    # Affective Memory: Table 1
    as.data.frame(summary(m1.Jones)[4])[10,1], 
    as.data.frame(summary(m2.Jones)[4])[10,1], 
    as.data.frame(summary(m3.Jones)[4])[10,1], 
    as.data.frame(summary(m4.Jones)[4])[10,1], 
    # Affective Memory: Table 2
    as.data.frame(summary(m5.Jones)[4])[10,1],
    as.data.frame(summary(m6.Jones)[4])[10,1],
    as.data.frame(summary(m7.Jones)[4])[10,1],
    as.data.frame(summary(m8.Jones)[4])[10,1],
    as.data.frame(summary(m9.Jones)[4])[10,1],
    as.data.frame(summary(m10.Jones)[4])[10,1],
    as.data.frame(summary(m11.Jones)[4])[10,1],
    # Table 3: Running Tally
    as.data.frame(summary(t1.Jones)[4])[10,1], 
    as.data.frame(summary(t5.Jones)[4])[10,1], 
    as.data.frame(summary(t10.Jones)[4])[10,1], 
    as.data.frame(summary(t14.Jones)[4])[10,1], 
    as.data.frame(summary(t15.Jones)[4])[10,1], 
    as.data.frame(summary(t18.Jones)[4])[10,1], 
    as.data.frame(summary(t21.Jones)[4])[10,1], 
    as.data.frame(summary(t25.Jones)[4])[10,1], 
    # Table 4: Running Tally
    as.data.frame(summary(t31.Jones)[4])[10,1], 
    as.data.frame(summary(t35.Jones)[4])[10,1], 
    as.data.frame(summary(t40.Jones)[4])[10,1], 
    as.data.frame(summary(t44.Jones)[4])[10,1], 
    as.data.frame(summary(t45.Jones)[4])[10,1], 
    as.data.frame(summary(t48.Jones)[4])[10,1], 
    as.data.frame(summary(t51.Jones)[4])[10,1], 
    as.data.frame(summary(t55.Jones)[4])[10,1], 
    # Table 5: : Running Tally
    as.data.frame(summary(t61.Jones)[4])[10,1],
    as.data.frame(summary(t65.Jones)[4])[10,1],
    as.data.frame(summary(t71.Jones)[4])[10,1],
    as.data.frame(summary(t75.Jones)[4])[10,1],
    as.data.frame(summary(t76.Jones)[4])[10,1],
    as.data.frame(summary(t81.Jones)[4])[10,1],
    as.data.frame(summary(t85.Jones)[4])[10,1],
    as.data.frame(summary(t86.Jones)[4])[10,1]
    ),
  Candidate = rep("Jones",nrow(data.p.Jones)),
  Model = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8", "m9", "m10", "m11", "t1", "t5", "t10", "t14", "t15", "t18", "t21", "t25", "t31", "t35", "t40", "t44", "t45", "t48", "t51", "t55", "t61", "t65", "t71", "t75", "t76", "t81", "t85", "t86")
)

#### Williams #### 
coefficients.Williams.table = data.frame(
  Coefficient = c(
    # Affective Memory: Table 1
    as.data.frame(summary(m1.Williams)[4])[10,1], 
    as.data.frame(summary(m2.Williams)[4])[10,1], 
    as.data.frame(summary(m3.Williams)[4])[10,1], 
    as.data.frame(summary(m4.Williams)[4])[10,1], 
    # Affective Memory: Table 2
    as.data.frame(summary(m5.Williams)[4])[10,1],
    as.data.frame(summary(m6.Williams)[4])[10,1],
    as.data.frame(summary(m7.Williams)[4])[10,1],
    as.data.frame(summary(m8.Williams)[4])[10,1],
    as.data.frame(summary(m9.Williams)[4])[10,1],
    as.data.frame(summary(m10.Williams)[4])[10,1],
    as.data.frame(summary(m11.Williams)[4])[10,1],
    # Table 3: Running Tally
    as.data.frame(summary(t1.Williams)[4])[10,1], 
    as.data.frame(summary(t5.Williams)[4])[10,1], 
    as.data.frame(summary(t10.Williams)[4])[10,1], 
    as.data.frame(summary(t14.Williams)[4])[10,1], 
    as.data.frame(summary(t15.Williams)[4])[10,1], 
    as.data.frame(summary(t18.Williams)[4])[10,1], 
    as.data.frame(summary(t21.Williams)[4])[10,1], 
    as.data.frame(summary(t25.Williams)[4])[10,1], 
    # Table 4: Running Tally
    as.data.frame(summary(t31.Williams)[4])[10,1], 
    as.data.frame(summary(t35.Williams)[4])[10,1], 
    as.data.frame(summary(t40.Williams)[4])[10,1], 
    as.data.frame(summary(t44.Williams)[4])[10,1], 
    as.data.frame(summary(t45.Williams)[4])[10,1], 
    as.data.frame(summary(t48.Williams)[4])[10,1], 
    as.data.frame(summary(t51.Williams)[4])[10,1], 
    as.data.frame(summary(t55.Williams)[4])[10,1], 
    # Table 5: : Running Tally
    as.data.frame(summary(t61.Williams)[4])[10,1],
    as.data.frame(summary(t65.Williams)[4])[10,1],
    as.data.frame(summary(t71.Williams)[4])[10,1],
    as.data.frame(summary(t75.Williams)[4])[10,1],
    as.data.frame(summary(t76.Williams)[4])[10,1],
    as.data.frame(summary(t81.Williams)[4])[10,1],
    as.data.frame(summary(t85.Williams)[4])[10,1],
    as.data.frame(summary(t86.Williams)[4])[10,1]
    ),
  Candidate = rep("Williams",nrow(data.p.Williams)), 
  Model = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8", "m9", "m10", "m11", "t1", "t5", "t10", "t14", "t15", "t18", "t21", "t25", "t31", "t35", "t40", "t44", "t45", "t48", "t51", "t55", "t61", "t65", "t71", "t75", "t76", "t81", "t85", "t86")
  )

#### all
coefficients.all.table = rbind(
  coefficients.Smith.table,
  coefficients.Wilson.table,
  coefficients.Jones.table,
  coefficients.Williams.table)

## exporting coefficients.all.table as spss datafile: BEGIN

### exporting coefficients.all.table as DF
coefficients.all.table.d = data.frame(coefficients.all.table)

### loading foreign
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(foreign)

### exporting df to SPSS
write.table(coefficients.all.table.d, "/Users/hectorbahamonde/RU/RA/Rick_Lau/Memory_Data/detailed_coefficients.txt", sep="\t")

## exporting coefficients.all.table as spss datafile: END


table.df = data.frame(
  Variable = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8", "m9", "m10", "m11", "t1", "t5", "t10", "t14", "t15", "t18", "t21", "t25", "t31", "t35", "t40", "t44", "t45", "t48", "t51", "t55", "t61", "t65", "t71", "t75", "t76", "t81", "t85", "t86"),
  Mean = c(
    mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m1"]), 
    mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m2"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m3"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m4"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m5"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m6"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m7"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m8"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m9"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m10"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="m11"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t1"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t5"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t10"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t14"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t15"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t18"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t21"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t25"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t31"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t35"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t40"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t44"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t45"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t48"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t51"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t55"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t61"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t65"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t71"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t75"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t76"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t81"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t85"]), 
mean(coefficients.all.table$Coefficient[coefficients.all.table$Model=="t86"]))
  )
```


### Detail
```{r , message=FALSE, warning=FALSE, echo=FALSE}
table.df
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}
## exporting coefficients.all.table as spss datafile: BEGIN

### loading foreign
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(foreign)

### exporting df to SPSS
write.table(table.df, "/Users/hectorbahamonde/RU/RA/Rick_Lau/Memory_Data/averaged_coefficients.txt", sep="\t")

## exporting coefficients.all.table as spss datafile: END

```


### All Memory
```{r , message=FALSE, warning=FALSE, echo=FALSE}
# All Memory
mean(table.df$Mean[1:11])
```


### All Tally
```{r , message=FALSE, warning=FALSE, echo=FALSE}
# All Tally
mean(table.df$Mean[12:35])
```